### 2017-02-08 CO750-ApproximationAlgorithmsTopics/assignments/assignment_01.tex
6a written up

%Pb
\subsection{b}
\begin{theorem}
There exists a tree $T' = (V,F)$ such that $d^T(u,v) \leq d^{T'}(u,v) \leq 4 d^T(u,v).$
\end{theorem}
\begin{proof}
Pick $v \in V$ with a parent $w \not \in V$ and contract edge $vw$ in $T$. Repeat until all nodes of $T$ are in $V$. Multiply by $4$ the weights on all remaining edges. Call the resulting tree $T'$. Note that clearly $d^{T'}(u,v) \leq 4d^T(u,v)$ as contracting only shortens the distances. Furthermore, in the worst case $d^{T'}(u,v) = 2^i \cdot 4$ if contraction results in contracting $u$ and $v$ right up to the cluster where they were separated (that is, contracting preserves the largest edge distance on the $uv$-path in $T$). But 
$$2^i \cdot 4 = 2^i + 2^i + 2^i + 2^i \geq d(S^u_{i-1}, S_i) + d(S^v_{i-1}, S_i) +  d(S^u_{i-1}, u) + d(S^v_{i-1}, v) = d^T(u,v).$$
Hence the theorem holds.
\end{proof}
\end{document}

>>>>

%Pb
\subsection{b}

\paragraph{}
Let $G = (V,E)$ be a metric graph with edge costs $c:E \rightarrow \R_+$ and requirements $r(u,v) \in \N$ for all $u,v \in V$. Consider the following algorithm, $\cA$, for the Generalized Steiner Network (GSN) problem:
\begin{enumerate}

\end{document}
